---
title: "Fix the title"
author: "Your Name Here"
date: "Add the date"
output: 
    html_notebook
---

### Question 1  

#### Select the element in 10th row and 5th column in `iris` dataset

```{r}
data(iris)

```
#### Select the Species column n `iris` dataset and print the last 5 rows of that column
```{r}

```


### Question 2  

#### Write a `for` loop that iterates over the numbers 1 to 10 and print the multiple of 3 (multiply the number by 3) if the number is less than 5 and print the multiple of 2 (multiply the number by 2) if the number if greater than or equal to 5.
```{r}

```

### Question 3   

#### Write a `while` loop that prints out random normal numbers with mean equal 1 and standard deviation 2 (use rnorm()) but stops (breaks) if you get a number bigger than 3. Do not change the value inside set.seeed.
```{r}
set.seed(184)

```

### Question 4  

#### Use a nested for loop that produces the following data frame. Name of the dataframe is Counting. (Variables are V1, V2, V3, and V4. So they are the column names. Number of rows are 3.) Identify the pattern to create the for loop.

| V1 | V2 | V3 | V4 |  
|:-- |:-- |:-- |:-- |
| 1 | 2 | 3 | 4 |  
| 2 | 3 | 4 | 5 |  
| 3 | 4 | 5 | 6 |  

```{r}

```

### Question 5    

#### Complete the following user define function to generate `n` random normal numbers with a given mean and standard deviation and plot a histogram of it. Do not change  the seed number in set.seed. You can use the function `hist` to plot the histogram.  
##### Then call the function to generate 1000 random normal numbers with mean 0 and standard deviation 1 and plot a histogram of it.

```{r}
set.seed(184)
plotNormal <- function(repitions, mean, sd){
  
}


```


